---
title: "Weight and BMI"
author: "Bruno Rodrigues"
date: '`r Sys.Date()`'
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
library("readr")
library("ggplot2")
poids <- read_csv("~/Documents/config_files/weight/poids.csv")

```

```{r, echo=FALSE}
poids$bmi <- poids$Poids/(1.75**2)
# par(mar=c(5,4,4,5)+.1)
# plot(poids$Date, poids$Poids, type="l", col="blue", lwd=2, ylim = c(70, 86), ylab = "Weight", xlab = "Date")
# par(new=TRUE)
# plot(poids$Date, poids$bmi, type="l", col="red",xaxt="n",yaxt="n",xlab="",ylab="")
# axis(4)
# mtext("BMI",side=4,line=3)
# legend("topright", col=c("blue", "red"), lty=1, legend = c("Weight", "BMI"))
# grid()

ggplot(poids, aes(Date, Poids)) +
  geom_point() + theme_minimal() +
  geom_smooth()


n_measur <- 60
```

Graph over the last `r n_measur` measurements:

```{r, echo=FALSE}
#par(mar=c(5,4,4,5)+.1)
n <- nrow(poids)
poidsLast <- poids[(n - n_measur):n,]
#plot(poidsLast$Date, poidsLast$Poids, type="l", col="blue", lwd=2, ylim = c(min(poidsLast$Poids), #max(poidsLast$Poids)), ylab = "Weight", xlab = "Date")

ggplot(poidsLast, aes(Date, Poids)) +
  geom_point() + theme_minimal() +
  geom_smooth()

```


Mean over the last 5 measurements:

```{r}
mean(tail(poids$Poids))
```

Last weight:

```{r}
tail(poids$Poids, n = 1)
```

Last bmi:

```{r}
tail(poids$bmi , n = 1)
```

Max weight ever `r max(poids$Poids)`kg (BMI: `r round(max(poids$bmi))`) on the 
`r poids$Date[which(poids$Poids == max(poids$Poids))]` and min weight ever 
`r min(poids$Poids)`kg (BMI: `r round(min(poids$bmi))`) on the 
`r poids$Date[which(poids$Poids == min(poids$Poids))]`.

Overall loss (max weight - last weight): 
`r max(poids$Poids) - tail(poids$Poids, n = 1)`kg.

Five last variations: `r tail(poids$Poids) - tail(poids$Poids[-length(poids$Poids)])`. (Total: `r sum(tail(poids$Poids) - tail(poids$Poids[-length(poids$Poids)]))`kg )

